\section{Experience}
\resumeSubHeadingListStart

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Platform Engineer}{Jan. 2024 -- Jun. 2024}
{Monash University, Public Cloud \& Observability}{Clayton, Melbourne}
\resumeItemListStart
\resumeItem{Developing IPAM-enabled VPC based Service Catalogue Product in AWS to provide pre-approved services for users}
\resumeItem{Developing and maintaining DevSecOps pipeline in Azure DevOps Cloudformation, Trivvy, Checkov, and Checkmarx}
\resumeItemListEnd

\resumeSubheading
{IAM Security Engineer}{Jan. 2024 -- Jun. 2024}
{Coles Group, Identity and Access Management}{Tooronga, Melbourne}
\resumeItemListStart
\resumeItem{Triaged incidents and tasks in Azure AD \& NetIQ eDirectory hybrid AD environment as BAU}
\resumeItem{Developed Python library and Ansible module for automating PKI certificate reporting and renewal using Venafi TLS Protect API, to speed up certificate renewal process by 190\%}
\resumeItemListEnd

\resumeSubheading
{Product Security Engineer}{Nov. 2023 -- Jan. 2024}
{Mercari, Product Security Engineering}{Roppongi, Tokyo}
\resumeItemListStart
\resumeItem{Conducted security design reviews and security testing, identified multiple sensitive data exposure vulnerabilities}
\resumeItem{Developed Golang-based L4 and L7 proxy (chaining) applications with custom OIDC based authn and authz mechanism}
\resumeItem{Deployed to production in GCP, through Terraform and CI/CD pipeline within GitHub Enterprise}
\resumeItem{Removed blocker for 3+ other projects to enable secure access to isolated network environments with IAP-like functionality}
\resumeItemListEnd

\resumeSubheading
{Systems Engineer}{Sep. 2022 -- Nov. 2023}
{Monash University, Infrastructure Platforms, Automation}{Clayton, Melbourne}
\resumeItemListStart
%\resumeItem{Heavily involved in the migration process of infrastructure automation software from Puppet to Ansible}
\resumeItem{Developed and maintaiend over 40 custom Ansible roles to migrate from Puppet Enterprise for infra automation}
\resumeItem{Developed Python script to batch convert 1500+ host configuration files from Puppet to Ansible (YAML)}
\resumeItem{Used Azure DevOps Pipeline, Podman, and Ansible Automation Platform to automate tests on Linux systems}
%\resumeItem{all aspects of the infrastructure including networking, compliance, security hardening, and application deployment/configuration}
\resumeItem{Implemented roles and configurations for SSSD, nftables, OpenSCAP/CIS benchmark, SELinux, Splunk, Falcon Sensor etc.}
\resumeItemListEnd

\resumeSubHeadingListEnd
