\section{Experience}
\resumeSubHeadingListStart

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Platform Engineer}{Jan. 2024 -- Jun. 2024}
{Monash University, Public Cloud \& Observability}{Clayton, Melbourne}
\resumeItemListStart
\resumeItem{Developing IPAM-enabled VPC related Service Catalogue Product in AWS to provide pre-approved services for users}
\resumeItem{Developing and maintaining DevSecOps pipeline in Azure DevOps Cloudformation, Trivvy, Checkov, and Checkmarx}
\resumeItemListEnd

\resumeSubheading
{IAM Security Engineer}{Jan. 2024 -- Jun. 2024}
{Coles Group, Identity and Access Management}{Tooronga, Melbourne}
\resumeItemListStart
\resumeItem{Triaged incidents and tasks in Azure AD \& NetIQ eDirectory hybrid AD environment as BAU}
\resumeItem{Developed a Python library and Ansible module for automating PKI certificate reporting and renewal using Venafi TLS Protect API, to speed up certificate renewal process by 190\%}
\resumeItemListEnd

\resumeSubheading
{Product Security Engineer}{Nov. 2023 -- Jan. 2024}
{Mercari}{Roppongi, Tokyo}
\resumeItemListStart
\resumeItem{Developed Golang-based L4 and L7 proxy (chaining) applications with custom OIDC based authn and authz mechanism}
\resumeItem{Deployed to production in GCP, through Terraform and CI/CD pipeline within GitHub Enterprise}
\resumeItem{Removed blocker for 3+ other projects to enable secure access to restricted environments with IAP-like auth mechanism}
\resumeItem{Performed ad-hoc security design reviews and security testing and identified multiple potential security vulnerabilities}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Dec. 2022 -- Present}
{Monash University}{Clayton, Melbourne}
\resumeItemListStart
\resumeItem{Optimisation of zk-SNARK zero-knowledge post quantum proof protocol}
\resumeItem{Modification of the \href{https://github.com/scipr-lab/libsnark/}{libsnark C++ library} it's dependencies, to add support for our custom security parameters}
%\resumeItem{Project currently under work - Details are omitted}
\resumeItemListEnd

\resumeSubheading
{Summer Vacation Research Scholarship Program}{Nov. 2022 -- Feb. 2023}
{Monash University}{Clayton, Melbourne}
\resumeItemListStart
\resumeItem{Developing a middlebox protocol that enables stateful traffic inspection on an encrypted communication}
\resumeItem{Currently being developed as a C++ library}
\resumeItem{Evaluating the performance of the protocol compared to the existing implementations}
%\resumeItem{Project currently under work - Details are omitted}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Oct. 2022 -- Dec. 2022}
{Monash University}{Clayton, Melbourne}
\resumeItemListStart
\resumeItem{Developed a secure database architecture utilising searchable symmetric encryption to enable insertion, storage, and query of data on an encrypted database}
\resumeItem{Developed with high performance in mind - parallelism achieved using Apache Spark (Java)}
\resumeItem{Evaluated the performance of the architecture with various input parameters}
%\resumeItem{Literature currently under review - Details are omitted}
\resumeItemListEnd

\resumeSubheading
{Systems Officer}{Sep. 2022 -- Present}
{Monash University}{Clayton, Melbourne}
\resumeItemListStart
\resumeItem{Heavily involved in the migration process of infrastructure automation software from Puppet to Ansible}
\resumeItem{Developing Ansible roles from Puppet modules and other custom roles to support additional configurations}
\resumeItem{Developing Python script to batch convert 1500+ host configuration files from Puppet to Ansible (YAML)}
\resumeItem{Utilising Azure DevOps Pipeline + Podman containers, Ansible Automation Platform to automate testing on Ubuntu, RHEL 7/8 systems}
\resumeItem{Includes automation in all aspects of the infrastructure including networking, compliance, security hardening, and application deployment/configuration}
\resumeItemListEnd

\resumeSubheading
{Research Assistant}{Apr. 2022 -- Oct. 2022}
{Monash University}{Clayton, Melbourne}
\resumeItemListStart
\resumeItem{Developed a .NET cryptography library for a post‐quantum lattice‐based public‐key cryptography algorithm}
\resumeItem{Completed C\# implementation of NIST PQC Round 3 NTRU Prime and NTRU algorithms from C reference implementations}
\resumeItem{Using C\# + .NET Framework Standard 2.0}
\resumeItem{Released as an open‐source library on \href{https://github.com/bcgit/bc-csharp}{Bouncy Castle's GitHub repository}}
\resumeItemListEnd

\resumeSubheading
{Winter Vacation Research Scholarship Program}{Jun. 2022 -- July.2022}
{Monash University}{Clayton, Melbourne}
\resumeItemListStart
\resumeItem{Literature review on various papers in following fields/topoics: stateful network functions and protocols, TCP protocol and TCP state machine, finite state machine, packet inspection (DPI), Function Secret Sharing (FSS), middleboxes, firewall, multi-party computation}
\resumeItemListEnd
\resumeSubHeadingListEnd
